The imputation methods big test

### 2020-04-27 pd2.Rmd
change getting dataset id from unstable results to median

  results[[1]]
  # change i bound to number of datasets 
  for (i in c(1, 2, 3, 5, 6, 7, 8, 9)){ # TUTAJ BANGLA DOPÓKI NIE WEŹMIE SIĘ KTÓREGOŚ ZE ZBIORÓW 4, 10, 11, 12, 13, 14 (czyli "nowych")
    kable(result_table(i), caption = paste("Dataset id: ", results[[1]][[i]]$dataset_id, sep = ""))
  }

@@

  kable(result_table(1), caption = paste("Dataset id: ", results[[1]][[1]]$dataset_id, sep = ""))
  kable(result_table(2), caption = paste("Dataset id: ", results[[1]][[2]]$dataset_id, sep = ""))
  kable(result_table(3), caption = paste("Dataset id: ", results[[1]][[3]]$dataset_id, sep = ""))
  #kable(result_table(4), caption = paste("Dataset id: ", results[[1]][[4]]$dataset_id, sep = ""))
  kable(result_table(5), caption = paste("Dataset id: ", results[[1]][[5]]$dataset_id, sep = ""))
  kable(result_table(6), caption = paste("Dataset id: ", results[[1]][[6]]$dataset_id, sep = ""))
  kable(result_table(7), caption = paste("Dataset id: ", results[[1]][[7]]$dataset_id, sep = ""))
  kable(result_table(8), caption = paste("Dataset id: ", results[[1]][[8]]$dataset_id, sep = ""))
  kable(result_table(9), caption = paste("Dataset id: ", results[[1]][[9]]$dataset_id, sep = ""))
  #kable(result_table(10), caption = paste("Dataset id: ", results[[1]][[10]]$dataset_id, sep = ""))
  #kable(result_table(11), caption = paste("Dataset id: ", results[[1]][[11]]$dataset_id, sep = ""))
  #kable(result_table(12), caption = paste("Dataset id: ", results[[1]][[12]]$dataset_id, sep = ""))
  #kable(result_table(13), caption = paste("Dataset id: ", results[[1]][[13]]$dataset_id, sep = ""))
  #kable(result_table(14), caption = paste("Dataset id: ", results[[1]][[14]]$dataset_id, sep = ""))
```

>>>>

  results[[1]]
  # change i bound to number of datasets 
  for (i in c(1, 2, 3, 5, 6, 7, 8, 9)){ # TUTAJ BANGLA DOPÓKI NIE WEŹMIE SIĘ KTÓREGOŚ ZE ZBIORÓW 4, 10, 11, 12, 13, 14 (czyli "nowych")
    kable(result_table(i), caption = paste("Dataset id: ", results[[2]][[i]]$dataset_id, sep = ""))
  }

@@

  kable(result_table(1), caption = paste("Dataset id: ", results[[2]][[1]]$dataset_id, sep = ""))
  kable(result_table(2), caption = paste("Dataset id: ", results[[2]][[2]]$dataset_id, sep = ""))
  kable(result_table(3), caption = paste("Dataset id: ", results[[2]][[3]]$dataset_id, sep = ""))
  #kable(result_table(4), caption = paste("Dataset id: ", results[[2]][[4]]$dataset_id, sep = ""))
  kable(result_table(5), caption = paste("Dataset id: ", results[[2]][[5]]$dataset_id, sep = ""))
  kable(result_table(6), caption = paste("Dataset id: ", results[[2]][[6]]$dataset_id, sep = ""))
  kable(result_table(7), caption = paste("Dataset id: ", results[[2]][[7]]$dataset_id, sep = ""))
  kable(result_table(8), caption = paste("Dataset id: ", results[[2]][[8]]$dataset_id, sep = ""))
  kable(result_table(9), caption = paste("Dataset id: ", results[[2]][[9]]$dataset_id, sep = ""))
  kable(result_table(10), caption = paste("Dataset id: ", results[[2]][[10]]$dataset_id, sep = ""))
  kable(result_table(11), caption = paste("Dataset id: ", results[[2]][[11]]$dataset_id, sep = ""))
  kable(result_table(12), caption = paste("Dataset id: ", results[[2]][[12]]$dataset_id, sep = ""))
  kable(result_table(13), caption = paste("Dataset id: ", results[[2]][[13]]$dataset_id, sep = ""))
  kable(result_table(14), caption = paste("Dataset id: ", results[[2]][[14]]$dataset_id, sep = ""))
```
